New lower bounds for Schur and weak Schur numbers

### 2021-06-12 article/weakschur.tex
modifs

\qquad In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
for weak Schur numbers of Abbott and Hanson's construction for Schur numbers. By analogy with the previous section,
we then introduce WSF-templates as well as an associated sequence \(\WS^+(n)\). We find templates and use them to
provide new lower bounds for weak Schur numbers.

@@

Given that \hyperref[Theorem3.1]{Theorem 3.1} will appear as a particular case of a more general theorem after the introduction of
templates for weak Schur numbers, we only give here an intuitive explanation of the demonstration; a formal
\hyperref[proof_theorem]{proof} can be found in the appendix.

@@

Like SF-templates, \(\mathcal{R}\) and \(\mathcal{C}\) play the role of security zones for each other. Note that with
this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to two the
sum of the columns modulo \(a\).

@@

In particular, taking \(w = l = \left\lceil \displaystyle \frac{q}{2} \right\rceil\) and \(r = \left\lfloor \displaystyle \frac{q}{2} \right\rfloor\) works, thus obtaining the above theorem.\\
\par
As in the previous section, we now introduce WSF-templates and the sequence \(\WS^+\) in order to generalize the above construction.

@@

\qquad In this subsection, we introduce WSF-templates and prove calculative results for the general construction 
theorem on templates for weak Schur numbers.

@@

\begin{sloppypar}
\(\pi\) is the projection on the first line mentioned in the intuitive explanation. The following four propositions are
calculative properties on \(\pi\) reflecting the behaviour of an element's column number in Figure \ref{SchemaWS} and
that we will use later when we introduce WSF-templates.
\end{sloppypar}

@@

Function \(\lambda\) maps an element \(x\) to its line number as mentioned in the intuitive explanation.
As we just did with \(\pi\), we proove three more results on both \(\pi\) and \(\lambda\) that will appear useful in
\hyperref[ConstructionWSF]{Subsection 3.3}.

@@

\noindent  if \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\) \\
\vspace{1mm}
\noindent if \(x \mod a \leqslant b\) then
\(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\) \\
\end{proof}

@@

\begin{definition}
Let \( (a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\). Let \((A_1,...,A_n)\) a partition of  \([\![1, a + b]\!]\).
This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WSF-template) with width \(a\) and \(n\) colors when :

@@

Please note that the special color \(n\) is not necessarily the last color by order of appearance.
We now introduce the number \(\WS^+(n)\) that plays the same role as \(\S^+(n)\) for SF-templates.
However, WSF-templates being more sophisticated than SF-templates, the definition of \(\WS^+(n)\)
is slighty more complicted.

\begin{definition}
Let \( (n,b) \in (\mathbb{N}^*)^2\). If there exists \(a\) such that there exists a \(b\)-WSF-template with width \(a\) 
and \(n\) colors, we define :
\[
\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there exists a } b \text{-WSF-template with width } a \text{ and } n \text{ colors} \}.
\]
If no such \(a\) exists, we set \(\WS_b^+(n) = 0\).
\end{definition}

@@

\begin{proof}[\textsc{Proof.}]
The lower bound comes from the analogous of Abott and Hanson's construction for weak Schur numbers.
The upper bound comes from the fact that a WSF-template with width \(a\) and \(n\) colors contains a partition of
\([\![1, a]\!]\) into \(n\) sum-free subsets. \\
\end{proof}

@@

\subsection{Construction of weak Schur partitions using WSF-templates}
\label{ConstructionWSF}

\begin{theorem}
\label{Theorem3.18}
Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\) 
into \(k\) sum-free subsets and a \(b\)-WSF-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors, 
then there exists a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
\end{theorem}

@@

\begin{remark}
In the SF-template construction for Schur numbers, the additive constant comes from the fact that the special color does
not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_{max}\) can actually be replaced by
\[
\max_{b \in \mathbb{N}^*} \left\{\min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}.
\]
\end{remark}

\begin{proof}[\textsc{Proof.}]
\begin{sloppypar}
Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \((p,k) \in (\mathbb{N}^*)^2\). Denote by \(f\) the coloring 
associated to the \(b\)-WSF-template  and \(g\) the one associated to the sum-free partition of \([\![1,p]\!]\); where 
\({f : [\![1, a + b]\!] \longrightarrow [\![1,n+1]\!]}\) and \({g : [\![1, p]\!]  \longrightarrow [\![1, k]\!]}\). Moreover, assume 
that the sum-free coloring of \([\![1, p]\!]\) is ordered.
\end{sloppypar}

\par
NB: To keep the notation short, the conditions \(x + y \leqslant p\)  and \(x + y \leqslant a + b\) are omitted in the following five predicates.
\par
The (weakly) sum-free conditions are expressed as:
\begin{equation}
\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
\begin{array}{l}
	f(x) = f(y) \\
	x \neq y
\end{array}
\right. \Longrightarrow f(x+y) \neq f(x)
\end{equation}
\begin{equation}
\forall (x,y) \in [\![b+1,a + b]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x),
\end{equation}
\begin{equation}
\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x).
\end{equation}

The additionnal constraints for the WSF-template are:
\begin{equation}
\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
\begin{array}{l}
	f(x) = f(y) \leqslant n \\
	x + y > a + b
\end{array}
\right. \Longrightarrow f(\pi(x+y)) \neq f(x),
\end{equation}
\begin{equation}
\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
\begin{array}{l}
	f(x) = f(y) = n + 1 \\
	x + y > 2 a + b
\end{array}
\right. \Longrightarrow f(x+y - 2 a) \neq f(x).
\end{equation}

Here, we consider \(\pi\) defined in \hyperref[DefinitionWS+]{subsection 3.2} as an application defined on \([\![b + 1, p a + b]\!]\). 
Split \([\![1, p a + b]\!]\) into three subsets.

@@

\noindent \underline{\textbf{Case 1:} \((x,y) \in \mathcal{T}^2\)}
\par
If \(x + y \leqslant b\) then \(h(x+y)=f(x+y)\). Otherwise, \(b < x+y < a+b\) since \(b < a\) and 
therefore \(\pi(x + y) = x +y\) (proposition \ref{prop1}). Hence in both cases \(h(x+y)=f(x+y)\). Given that 
\(f\) is a weakly sum-free coloring, \(f(x + y) \neq f(x)\) since \(f(x)=h(x)=h(y)=f(y)\) and \(x \neq y \). That 
is \(h(x + y) \neq h(x)\). \\

\noindent \underline{\textbf{Case 2:} \((x,y) \in \mathcal{T} \times \mathcal{C}\)}
\par
Given that \(h(x) = h(y)\) and by definition of \(h\), \(f(x) = f(\pi(y))\). Besides, \(f(\pi(y)) \leqslant n\) since 
\(y \in \mathcal{C}\). Two cases are to be distinguished according to the value of \(x + \pi(y)\).
\begin{itemize}
\item \begin{sloppypar}
	If \(x + \pi(y) \leqslant a + b\) then \(f(x + \pi(y)) = f(\pi(x + y))\) (\hyperref[prop3]{Proposition 3.7}). Given that \(f\) is 
	a weakly sum-free coloring, \(f(x+\pi(y)) \neq f(x)\) since \(f(x)=f(\pi(y))\) and \(x \neq \pi(y)\) since
	\({x \leqslant b < \pi(y)}\).
	\end{sloppypar}
\item \begin{sloppypar}
	If \(x+\pi(y)> a+b\) then given that \(f\) is a WSF-template and since \({f(x) = f(\pi(y)) \leqslant n}\), 
	\({f(\pi(x+\pi(y))) \neq f(x)}\).~Furthermore \({f(\pi(x+\pi(y))) = f(\pi(x+y))}\) (\hyperref[prop2]{Proposition 3.6}), such that 
	\({f(\pi(x+ y)) \neq f(x)}\).
	\end{sloppypar}
\end{itemize}
\par
Hence in both cases \(f(\pi(x+y)) \neq f(x)\). If  \(f(\pi(x+y)) \leqslant n\) then \(h(x+y) = f(\pi(x+y))\). Therefore 
\(h(x+y) \neq h(x)\) since \(f(x) = h(x)\). Otherwise, \(f(\pi(x+y)) = n + 1\) and thus \(h(x+y) > n\). In particular, 
\(h(x + y) \neq h(x)\) since \(h(x) = h(y) \leqslant n\). \\

@@

\noindent \underline{\textbf{Case 4:} \((x,y) \in \mathcal{C}^2\)}
\par
By definition of \(h\) and since \(h(x)=h(y)\), \(f(\pi(x)) = f(\pi(y))\). Two cases are to be distinguished according 
to the value of \(\pi(x)+\pi(y)\).
\begin{itemize}
\item If \(\pi(x) + \pi(y) \leqslant a+b\) then \(\pi(x)+\pi(y) = \pi(x + y)\). Hence \(f(\pi(x + y)) \neq f(\pi(x))\) since 
	\(f\) is sum-free for \(x>b\)
\item \begin{sloppypar} 
	If \(\pi(x)+\pi(y)>a+b\) then given that \(f\) is a WSF-template, \({f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x))}\) since 
	\({f(\pi(x)) = f(\pi(y))}\). Besides,  \({f(\pi(\pi(x)+\pi(y))) = f(\pi(x + y))}\) (\hyperref[prop4]{Proposition 3.8}). Hence \({f(\pi(x + y)) 
	\neq  f(\pi(x))}\).
	\end{sloppypar}
\end{itemize}
\par
Hence in both cases \(f(\pi(x+y)) \neq f(x)\). If  \(f(\pi(x+y)) \leqslant n\) then \(h(x+y) = f(\pi(x+y))\). Therefore 
\(h(x+y) \neq h(x)\) since \(f(x) = h(x)\). Otherwise, \(f(\pi(x+y)) = n + 1\) and thus \(h(x+y) > n\). In particular, 
\(h(x + y) \neq h(x)\) since \(h(x) = h(y) \leqslant n\). \\

@@

\noindent \underline{\textbf{Case 6:} \((x,y) \in \mathcal{R}^2\)}
\par
In particular \(f(\pi(x)) = f(\pi(y))=n + 1\). Three cases are to be distinguished according to the value of \(\pi(x) + \pi(y)\).
\begin{itemize}
\item If \(\pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!]\) then \(\lambda(x + y) = \lambda(x) + \lambda(y)\) 
	(\hyperref[prop7]{Proposition 3.12}). By definition of \(h\) and since \(h(x) = h(y)\), \(g(\lambda(x)) = g(\lambda(y))\).
	Hence, \(h(\lambda(x + y)) \neq h(\lambda(x))\) since \(h\) is a sum-free coloring. If \(f(x+y) \geqslant n + 1\) 
	then \(h(x + y) = n + g(\lambda(x + y))\). And \(h(x) = n + g(\lambda(x))\). Therefore, \(h(x + y)  \neq h(x)\). 
	Otherwise \(h(x+y) \leqslant n < h(x)\). In particular \(h(x + y) \neq h(x)\).
\item If \(\pi(x)+\pi(y)>2a+b\) then \(f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x)) = n + 1\) since \(f\) is a \(b\)-WSF template and 
	\(f(\pi(x)) = f(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (\hyperref[prop4]{Proposition 3.8}), \(f(\pi(x+y)) \neq n + 1\).
\item \begin{sloppypar}
	If \(\pi(x)+\pi(y)\leqslant b+a\) then, given that \(\pi(x)+\pi(y) \geqslant b\) and \(f_{| [\![b, a + b ]\!]}\) is 
	sum-free, \({f(\pi(x) + \pi(y)) \neq f(\pi(x)) = n + 1}\). That is \({f(\pi(x + y)) \neq n + 1}\) (\hyperref[prop1]{Proposition 3.5}).
	\end{sloppypar}
\end{itemize}
\par
In both of the last two cases, \({f(\pi(x + y)) \neq n + 1}\) that is \(x+y \in \mathcal{C}\). Therefore \(h(x+y) < n \leqslant h(x)\). 
In particular, \(h(x + y) \neq h(x)\). \\
\end{proof}

The general lower bound for weak Schur numbers in function of both regular and weak Schur numbers can be seen as a particular
case of WSF-template in the same way Abott and Hanson's construction can be seen as a particular case of SF-template. Acutally,
like for SF-templates, the additive constant of a WSF-template can be improved by weakening the hypotheses made on
the last row. The principle behind it is the same as in the analogous proposition for SF-templates.

\begin{proposition}
Let \((b, k, a) \in (\mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WSF-template with width \(p\) and \(k\) colors. Let
\(c \in \mathbb{N}\) and assume there there exists a coloring \(g\) of \([\![b + 1, b + c]\!]\) with \(k\) colors such that for all \(c \in [\![1, k]\!]\),

@@

The WSF-templates can actually be fine-tuned further. However, it gives only minor improvements (most likely only an additive
constant) at the cost of dramatically increasing the size of the search space. Therefore, it does not seem relevant to
use this sophistications given that we could not even find good WSF-templates with five colors using a computer (here good
means better than those obtain by combining smaller templates).

@@

\par
To sum up, one can look for a generalised WSF-template that uses a special coloring for the tail and the first row, a
coloring dedicated to the rows whose number is not 1 but is in the first color in the sum-free partition, a coloring for all
the other rows and a special coloring for the last numbers (as previously explained for the improvement of the additive
constant of WSF-templates).

@@

\begin{theorem}
\label{Theorem3.22}
Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\) . If there exists a SF-template with width 
\(p\) and \(k+1\) colors and a \(b\)-WSF-template with width \(a\) and \(n\) colors, then there exists a \(pb\)-WSF-template 
with width \(pq\) and \((n+k)\) colors.
\end{theorem}

\hyperref[Theorem3.22]{Theorem 3.22} yields the following corollary.

\begin{proof}[\textsc{Proof.}]
The idea is the same as in the previous theorem. The only difference is the WSF property inherited
from the WSF-template. \\
\end{proof}

@@

\qquad We exhibited WSF-templates using a SAT solver, hence providing lower bound on \(WS^+\) and inequalities 
of the type \(WS(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
\((a, b)\) (in the lexicographic order). As we will see, this way of computing lower bounds is not necessarily the best
we can do. In the following, we give the strongest inequalities we have so far and further insight about how they were produced.

@@

(\ref{WS(n+1)}) and (\ref{WS(n+2)}) were already found by Rowley, they are detailed in \cite{RowleyWS}. (\ref{WS(n+3)}) is optimal 
and was found with a SAT solver. It uses the first sophistication explained in the \hyperref[ConstructionWSF]{Subsection 3.3} in order to add 
the last number in the first color. The \hyperref[WSF-templates]{corresponding template} can be found in the appendix.
As for (\ref{WS(n+4)}), it was obtained by combining an optimal SF-template with width 33 with a WSF-template with width 4.
The best template we could get with a computer search gives the inequality \(\WS(n+4) \geqslant 127 S(n) + 68\).
It was also found with the SAT solver. In order to reduce the search space, we only looked for WSF-templates of
five colors which start with a good \(\WS(4)\) partition and we assumed that the special color was the last by order of 
appearance. However, this approach most likely prevents us from finding the best WSF-templates
as we explain in the next subsection for weakly sum-free partitions. We highly suspect that there exists more efficient WSF-templates
with \(n \geqslant 5\) colors. One may try to go over a different search space using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}.
This could be the suject of a future work. Further details about the encoding as a SAT problem can be found in \cite{Heule2017}.

Like in Subsection 2.3 \textbf{LABEL NECESSAIRE}, we compute the lower bounds given by (\ref{WS(n+1)}), 
(\ref{WS(n+2)}) and (\ref{WS(n+3)}) for \( n \in [\![8,15]\!] \). The best lower bound
for each integer is highlighted.

@@

With \( S(9) \geqslant 17\,803 \), we found a new lower bound for \(\WS(10)\) using (\ref{WS(n+1)}).
Moreover, (\ref{WS(n+3)}) gives new lower bounds for \(\WS(9)\) and \(WS(14)\).

\subsection{Conclusion on WSF-templates}

>>>>

\qquad In this section, we generalize Rowley's constructions for weak Schur numbers \cite{RowleyWS} and give an analogous
for weak Schur numbers of Abbott and Hanson's construction for Schur numbers. By analogy with the previous section,
we then introduce WS-templates as well as an associated sequence \(\WS^+(n)\). We find templates and use them to
provide new lower bounds for weak Schur numbers.

@@

Given that \hyperref[Theorem3.1]{Theorem 3.1} will appear as a particular case of a more general theorem after the introduction of
templates for weak Schur numbers, we only give here an intuitive explanation of the demonstration; a formal
\hyperref[PreuveThm]{proof} using templates for weak Schur numbers is provided.

@@

Like S-templates, \(\mathcal{R}\) and \(\mathcal{C}\) play the role of security zones for each other. Note that with
this numbering of columns, the column of the sum of two numbers is the only integer in \([\![-l,q]\!]\) equal to two the
sum of the columns modulo \(a\).

@@

In particular, taking \(w = l = \left\lceil \displaystyle \frac{q}{2} \right\rceil\) and \(r = \left\lfloor \displaystyle \frac{q}{2} \right\rfloor\) works, thus obtaining the above theorem.\\
\par
As in the previous section, we now introduce WS-templates and the sequence \(\WS^+\) in order to generalize the above construction.

@@

\qquad In this subsection, we introduce WS-templates and prove calculative results for the general construction
theorem on templates for weak Schur numbers.

@@

\begin{sloppypar}
\(\pi\) is the projection on the first line mentioned in the intuitive explanation. The following four propositions are
calculative properties on \(\pi\) reflecting the behaviour of an element's column number in Figure \ref{SchemaWS} and
that we will use later when we introduce WS-templates.
\end{sloppypar}

@@

Function \(\lambda\) maps an element \(x\) to its line number as mentioned in the intuitive explanation.
As we just did with \(\pi\), we proove three more results on both \(\pi\) and \(\lambda\) that will appear useful in
\hyperref[ConstructionWS]{Subsection 3.3}.

@@

\begin{itemize}
\item if \(x \mod a>b\) then \(a\lambda(x)+\pi(x)-a=a\left\lfloor\dfrac{x}{a}\right\rfloor+x \mod a=x\)
\item if \(x \mod a \leqslant b\) then \(a\lambda(x)+\pi(x)-a=a \left( \left \lfloor \dfrac{x}{a} \right \rfloor - 1 \right)+x \mod a +a=x\)
\end{itemize}
\end{proof}

@@

\begin{definition}
Let \( (a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\). Let \((A_1,...,A_n)\) a partition of  \([\![1, a + b]\!]\).
This partition is said to be a \(b\)-weakly-sum-free template (\(b\)-WS-template) with width \(a\) and \(n\) colors when :

@@

Please note that the special color \(n\) is not necessarily the last color by order of appearance.
We now introduce the number \(\WS^+(n)\) that plays the same role as \(S^+(n)\) for S-templates.
However, WS-templates being more sophisticated than S-templates, the definition of \(\WS^+(n)\)
is slighty more complicted.

\begin{definition}
Let \( (n,b) \in (\mathbb{N}^*)^2\). If there exists \(a\) such that there exists a \(b\)-WS-template with width \(a\)
and \(n\) colors, we define :
\[
\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there exists a } b \text{-WS-template with width } a \text{ and } n \text{ colors} \}.
\]
If no such \(a\) exists, we set \(\WS_b^+(n) = 0\).
\end{definition}

@@

\begin{proof}[\textsc{Proof.}]
The lower bound comes from the analogous of Abott and Hanson's construction for weak Schur numbers.
The upper bound comes from the fact that a WS-template with width \(a\) and \(n\) colors contains a partition of
\([\![1, a]\!]\) into \(n\) sum-free subsets. \\
\end{proof}

@@

\subsection{Construction of weak Schur partitions using WS-templates}
\label{ConstructionWS}

\begin{theorem}
\label{Theorem3.18}
Let \((a,n,b) \in (\mathbb{N}^*)^3\) with \(a > b\) and \( (p,k) \in (\mathbb{N}^*)^2\). If there exists a partition of \([\![1,p]\!]\)
into \(k\) sum-free subsets and a \(b\)-WS-template \((A_1,...,A_{n+1})\) with width \(a\) and \(n+1\) colors,
then there exists a partition of \([\![1, p a + b]\!]\) into \(k+n\) weakly sum-free subsets.
\end{theorem}

@@

\begin{remark}
In the S-template construction for Schur numbers, the additive constant comes from the fact that the special color does
not necessarily appear right at the begining of the repeating pattern. Likewise, \(b_{max}\) can actually be replaced by
\[
\max_{b \in \mathbb{N}^*} \left\{\min (A_{n+1} \backslash [\![1, b ]\!]) - 1~|~ \WS_b^+(n+1) = \WS^+(n+1) \right\}.
\]
\end{remark}

\begin{proof}[\textsc{Proof.}]
\begin{sloppypar}
Let \((a,n,b) \in (\mathbb{N}^*)^3\) and \((p,k) \in (\mathbb{N}^*)^2\). Denote by \(f\) the coloring
associated to the \(b\)-WS-template  and \(g\) the one associated to the sum-free partition of \([\![1,p]\!]\); where
\({f : [\![1, a + b]\!] \longrightarrow [\![1,n+1]\!]}\) and \({g : [\![1, p]\!]  \longrightarrow [\![1, k]\!]}\). Moreover, assume
that the sum-free coloring of \([\![1, p]\!]\) is ordered.
\end{sloppypar}

\par
NB: To keep the notation short, the conditions \(x + y \leqslant p\)  and \(x + y \leqslant a + b\) are omitted in the following five predicates.
\par
The (weakly) sum-free conditions are expressed as:
\begin{equation}
\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
\begin{array}{l}
	f(x) = f(y) \\
	x \neq y
\end{array}
\right. \Longrightarrow f(x+y) \neq f(x),
\end{equation}
\begin{equation}
\forall (x,y) \in [\![b+1,a + b]\!]^2, f(x) = f(y) \Longrightarrow f(x+y) \neq f(x),
\end{equation}
\begin{equation}
\forall (x,y) \in [\![1,p]\!]^2, g(x) = g(y) \Longrightarrow g(x+y) \neq g(x).
\end{equation}

The additionnal constraints for the WS-template are:
\begin{equation}
\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
\begin{array}{l}
	f(x) = f(y) \leqslant n \\
	x + y > a + b
\end{array}
\right. \Longrightarrow f(\pi(x+y)) \neq f(x),
\end{equation}
\begin{equation}
\forall (x,y) \in [\![1,a + b]\!]^2, \left\{
\begin{array}{l}
	f(x) = f(y) = n + 1 \\
	x + y > 2 a + b
\end{array}
\right. \Longrightarrow f(x+y - 2 a) \neq f(x).
\end{equation}

Split \([\![1, p a + b]\!]\) into three subsets. \\
NB: To keep the notation short, the restriction to \([\![b + 1, p a + b]\!]\) of \(\pi\) defined in \hyperref[DefinitionWS+]{Subsection 3.2}
is denoted by \(pi\) in the hereunder equations.

@@

\noindent \underline{\textbf{Case 1:} \((x,y) \in \mathcal{T}^2\)}
\par
If \(x + y \leqslant b\) then \(h(x+y)=f(x+y)\). Otherwise, \(b < x+y < a+b\) since \(b < a\) and
therefore \(\pi(x + y) = x +y\) (\hyperref[prop1]{Proposition 3.5}). Hence in both cases \(h(x+y)=f(x+y)\). Given that
\(f\) is a weakly sum-free coloring, \(f(x + y) \neq f(x)\) since \(f(x)=h(x)=h(y)=f(y)\) and \(x \neq y \). That
is \(h(x + y) \neq h(x)\). \\

\noindent \underline{\textbf{Case 2:} \((x,y) \in \mathcal{T} \times \mathcal{C}\)}
\par
Given that \(h(x) = h(y)\) and by definition of \(h\), \(f(x) = f(\pi(y))\). Besides, \(f(\pi(y)) \leqslant n\) since
\(y \in \mathcal{C}\). Two cases are to be distinguished according to the value of \(x + \pi(y)\).
\begin{itemize}
\item \begin{sloppypar}
	If \(x + \pi(y) \leqslant a + b\) then \(f(x + \pi(y)) = f(\pi(x + y))\) (\hyperref[prop3]{Proposition 3.7}). Given that \(f\) is
	a weakly sum-free coloring, \(f(x+\pi(y)) \neq f(x)\) since \(f(x)=f(\pi(y))\) and \(x \neq \pi(y)\) since
	\({x \leqslant b < \pi(y)}\).
	\end{sloppypar}
\item \begin{sloppypar}
	If \(x+\pi(y)> a+b\) then given that \(f\) is a WS-template and since \({f(x) = f(\pi(y)) \leqslant n}\),
	\({f(\pi(x+\pi(y))) \neq f(x)}\).~Furthermore \({f(\pi(x+\pi(y))) = f(\pi(x+y))}\) (\hyperref[prop2]{Proposition 3.6}), such that
	\({f(\pi(x+ y)) \neq f(x)}\).
	\end{sloppypar}
\end{itemize}
\par
Hence in both cases \(f(\pi(x+y)) \neq f(x)\). If  \(f(\pi(x+y)) \leqslant n\) then \(h(x+y) = f(\pi(x+y))\). Therefore
\(h(x+y) \neq h(x)\) since \(f(x) = h(x)\). Otherwise, \(f(\pi(x+y)) = n + 1\) and thus \(h(x+y) > n\). In particular,
\(h(x + y) \neq h(x)\) since \(h(x) = h(y) \leqslant n\). \\

@@

\noindent \underline{\textbf{Case 4:} \((x,y) \in \mathcal{C}^2\)}
\par
By definition of \(h\) and since \(h(x)=h(y)\), \(f(\pi(x)) = f(\pi(y))\). Two cases are to be distinguished according
to the value of \(\pi(x)+\pi(y)\).
\begin{itemize}
\item If \(\pi(x) + \pi(y) \leqslant a+b\) then \(\pi(x)+\pi(y) = \pi(x + y)\). Hence \(f(\pi(x + y)) \neq f(\pi(x))\) since
	\(f\) is sum-free for \(x>b\)
\item \begin{sloppypar}
	If \(\pi(x)+\pi(y)>a+b\) then given that \(f\) is a WS-template, \({f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x))}\) since
	\({f(\pi(x)) = f(\pi(y))}\). Besides,  \({f(\pi(\pi(x)+\pi(y))) = f(\pi(x + y))}\) (\hyperref[prop4]{Proposition 3.8}). Hence \({f(\pi(x + y))
	\neq  f(\pi(x))}\).
	\end{sloppypar}
\end{itemize}
\par
Hence in both cases \(f(\pi(x+y)) \neq f(x)\). If  \(f(\pi(x+y)) \leqslant n\) then \(h(x+y) = f(\pi(x+y))\). Therefore
\(h(x+y) \neq h(x)\) since \(f(x) = h(x)\). Otherwise, \(f(\pi(x+y)) = n + 1\) and thus \(h(x+y) > n\). In particular,
\(h(x + y) \neq h(x)\) since \(h(x) = h(y) \leqslant n\). \\

@@

\noindent \underline{\textbf{Case 6:} \((x,y) \in \mathcal{R}^2\)}
\par
In particular \(f(\pi(x)) = f(\pi(y))=n + 1\). Three cases are to be distinguished according to the value of \(\pi(x) + \pi(y)\).
\begin{itemize}
\item If \(\pi(x) + \pi(y) \in [\![a + b + 1, 2 a + b]\!]\) then \(\lambda(x + y) = \lambda(x) + \lambda(y)\)
	(\hyperref[prop7]{Proposition 3.12}). By definition of \(h\) and since \(h(x) = h(y)\), \(g(\lambda(x)) = g(\lambda(y))\).
	Hence, \(h(\lambda(x + y)) \neq h(\lambda(x))\) since \(h\) is a sum-free coloring. If \(f(x+y) \geqslant n + 1\)
	then \(h(x + y) = n + g(\lambda(x + y))\). And \(h(x) = n + g(\lambda(x))\). Therefore, \(h(x + y)  \neq h(x)\).
	Otherwise \(h(x+y) \leqslant n < h(x)\). In particular \(h(x + y) \neq h(x)\).
\item If \(\pi(x)+\pi(y)>2a+b\) then \(f(\pi(\pi(x)+\pi(y))) \neq f(\pi(x)) = n + 1\) since \(f\) is a \(b\)-WS template and
	\(f(\pi(x)) = f(\pi(y))\). Given that \(\pi(\pi(x)+\pi(y)) = \pi(x+y)\) (\hyperref[prop4]{Proposition 3.8}), \(f(\pi(x+y)) \neq n + 1\).
\item \begin{sloppypar}
	If \(\pi(x)+\pi(y)\leqslant b+a\) then, given that \(\pi(x)+\pi(y) \geqslant b\) and \(f_{| [\![b, a + b ]\!]}\) is
	sum-free, \({f(\pi(x) + \pi(y)) \neq f(\pi(x)) = n + 1}\). That is \({f(\pi(x + y)) \neq n + 1}\) (\hyperref[prop1]{Proposition 3.5}).
	\end{sloppypar}
\end{itemize}
\par
In both of the last two cases, \({f(\pi(x + y)) \neq n + 1}\) that is \(x+y \in \mathcal{C}\). Therefore \(h(x+y) < n \leqslant h(x)\).
In particular, \(h(x + y) \neq h(x)\). \\
\end{proof}

There is a construction theorem for S-templates as well.

\begin{theorem}
\label{Theorem3.21}
Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there exists a S-template with width
\(p\) and \(k+1\) colors and a \(b\)-WS-template with width \(a\) and \(n\) colors, then there exists a \(pb\)-WS-template
with width \(pq\) and \((n+k)\) colors.
\end{theorem}

\hyperref[Theorem3.21]{Theorem 3.21} yields the following corollary.

\begin{proof}[\textsc{Proof.}]
The idea is the same as in the previous theorem. The only difference is the WS property inherited
from the WS-template. \\
\end{proof}

\hyperref[Theorem3.1]{Theorem 3.1} can be seen as a particular case of WS-template in the same way Abott and Hanson's 
construction can be seen as a particular case of S-template.

\begin{proof}[\textsc{Proof of \hyperref[Theorem3.1]{Theorem 3.1}.}]
\label{PreuveThm}
\textbf{REFORMULER LA PREUVE EN TERMES DE WS-TEMPLATES.} \\
\end{proof}

As in \hyperref[Corollary2.5]{Corollary 2.5}, the additive constant \hyperref[Theorem3.18]{Theorem 3.18} can be improved 
by weakening the hypotheses made on the last row. The principle behind it is the same as in \hyperref[Proposition2.6]{Proposition2.6}.

\begin{proposition}
Let \((b, k, a) \in (\mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WS-template with width \(p\) and \(k\) colors. Let
\(c \in \mathbb{N}\) and assume there there exists a coloring \(g\) of \([\![b + 1, b + c]\!]\) with \(k\) colors such that for all \(c \in [\![1, k]\!]\),

@@

The WS-templates can actually be fine-tuned further. However, it only gives minor improvements (most likely only an additive
constant) at the cost of dramatically increasing the size of the search space. Therefore, it does not seem relevant to
use this sophistications given that we could not even find good WS-templates with five colors using a computer (here good
means better than those obtain by combining smaller templates).

@@

\par
To sum up, one can look for a generalised WS-template that uses a special coloring for the tail and the first row, a
coloring dedicated to the rows whose number is not 1 but is in the first color in the sum-free partition, a coloring for all
the other rows and a special coloring for the last numbers (as previously explained for the improvement of the additive
constant of WS-templates).

@@

@@

\qquad We produced WS-templates using a SAT solver, hence providing lower bound on \(WS^+\) and inequalities
of the type \(WS(n+k) \geqslant a S(n) + b\). We sought templates providing the greatest value of \((a, b)\) (in the 
lexicographic order). Details concerning the encoding as a SAT problem can be found in \cite{Heule2017}.

\par
Here are the inequalities given by the current best WS-templates (to our knowledge). The \hyperref[WS-templates]{templates} 
corresponding to the third inequality can be found in the appendix.

@@

Inequalities (\ref{WS(n+1)}) and (\ref{WS(n+2)}) were found by Rowley, they are detailed in \cite{RowleyWS}. 
Inequality (\ref{WS(n+3)}) is cannot be further improved and was found with a SAT solver. It uses the first 
sophistication explained in the \hyperref[ConstructionWS]{Subsection 3.3} in order to add
the last number in the first color. As for inequality (\ref{WS(n+4)}), it was obtained by combining a S-template with 
width 33 with a WS-template with width 4. The best template we could find with a computer search gives the 
inequality \(\WS(n+4) \geqslant 127 S(n) + 68\). It was also found with the SAT solver. In order to reduce the search space, 
we only looked for WS-templates of five colors which start with a near-optimal \(\WS(4)\) partition and we assumed that the 
special color was the last by order of appearance. We highly suspect that bettert WS-templates with \(n \geqslant 5\) 
colors can be found but one would have not to use the above assumptions. One may try to go over a different search space 
using a Monte-Carlo method, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.

Like in \hyperref[Subsection2.3]{Subsection 2.3}, we compute the lower bounds given by inequalities (\ref{WS(n+1)}),
(\ref{WS(n+2)}) and (\ref{WS(n+3)}) for \( n \in [\![8,15]\!] \). The best lower bound for each value of \(n\) is highlighted.

@@

With \( S(9) \geqslant 17\,803 \), we found a new lower bound for \(\WS(10)\) using (\ref{WS(n+1)}).
Moreover, inequality (\ref{WS(n+3)}) gives new lower bounds for \(\WS(9)\) and \(WS(14)\).

\subsection{Conclusion on WS-templates}
